Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-24 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Related Work added
Closes #2

>>>>

Other works employ the use of No SQL databases, the work of Seyama and Munetomo \cite{seyama2016development}
employs in their implementation a Platform as-a Service (PaaS) and NoSQL database to facilitate collaboration 
among a large number of users for the interactive modelling of 3D glasess.  This system reduces the user fatigue
by using a collaborative filtering algorithm to show the information searched for and utilized by similar users.
